---
title: "Agricultural Production Statistics in New Zealand: Total number of sheep in New Zealand (1935-2024)"
subtitle: "due Wednesday, September 30, 2026"
author: "Isaiah Moliga-Puletasi"
format: html
execute: 
  warning: false
  message: false
---
Citation: This dataset comes from TidyTuesday's 2-17-26 weekly data challenge, [Agricultural Production Statistics in New Zealand
](https://github.com/rfordatascience/tidytuesday/blob/main/data/2026/2026-02-17/readme.md), curated by Jen Richmond. The [data](https://datainfoplus.stats.govt.nz/item/nz.govt.stats/eb7208cf-2f0f-416a-bd77-2fdbb9043255?_ga=2.264735308.2106648024.1715287902-1399521469.1678132138) is dervied from Figure.NZ.

Description: The Agricultural Production Statistics in New Zealand dataset provides quantitative information on New Zealand's agricultural systems. By collecting agricultural data in New Zealand, we can see the human-agriculture relations that arise over time. This dataset is particulary interested in the decline of sheep populations relative to humans over. 

```{r}
library(tidyverse)
```

```{r}
dataset <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2026/2026-02-17/dataset.csv')

new_dataset <- dataset |>
    dplyr::filter(measure == "Total Sheep") |>
    dplyr::select(year_ended_june, measure, value)

new_dataset |> 
    ggplot(aes(x = year_ended_june, y = value)) +
    geom_line() + 
    labs(
        title = "Total number of sheep in New Zealand (1935-2024)",
        x = "Year",
        y = ""
    )
new_dataset
```

